Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models

### 2020-10-23 A-BasicCommom/CVPR2021/cvpr_classification.tex
1. Fix and update template.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{cpvr_classification}
}

>>>>

{\small
\bibliographystyle{ieee_fullname}
%\bibliography{cpvr_classification}
\begin{thebibliography}{10}

  \bibitem{lee2009convolutional}
Lee, H., Grosse, R., Ranganath, R. \&  Ng, A.~Y.
\newblock {Convolutional deep belief networks for scalable unsupervised
  learning of hierarchical representations}.
\newblock In {\em Proceedings of the 26th annual international conference on
  machine learning}, pages 609--616, 2009.

\bibitem{nair2010rectified}
Nair, V. \&  Hinton, G.~E.
\newblock {Rectified linear units improve restricted boltzmann machines}.
\newblock In {\em ICML}, 2010.

\bibitem{mikolov2013distributed}
Mikolov, T., Sutskever, I., Chen, K., Corrado, G.~S. \&  Dean, J.
\newblock {Distributed representations of words and phrases and their
  compositionality}.
\newblock In {\em Advances in neural information processing systems}, pages
  3111--3119, 2013.

\bibitem{devlin2019bert}
Devlin, J., Chang, M.-W., Lee, K. \&  Toutanova, K.
\newblock {BERT: Pre-training of Deep Bidirectional Transformers for Language
  Understanding}.
\newblock In {\em NAACL-HLT (1)}, 2019.

\bibitem{vincent2008extracting}
Vincent, P., Larochelle, H., Bengio, Y. \&  Manzagol, P.-A.
\newblock {Extracting and composing robust features with denoising
  autoencoders}.
\newblock In {\em Proceedings of the 25th international conference on Machine
  learning}, pages 1096--1103, 2008.

\bibitem{chen2020generative}
Chen, M., Radford, A., Child, R., Wu, J., Jun, H., Dhariwal, P., Luan, D.
 and Sutskever, I.
\newblock {Generative Pretraining from Pixels}.
\newblock In {\em Proceedings of the 37th International Conference on Machine
  Learning}, 2020.

\bibitem{wang2019development}
Wang, W., Yang, Y., Wang, X., Wang, W. \&  Li, J.
\newblock {Development of convolutional neural network and its application in
  image classification: a survey}.
\newblock {\em Optical Engineering}, 58(4):40901, 2019.

\bibitem{lecun1990handwritten}
LeCun, Y., Boser, B.~E., Denker, J.~S., Henderson, D., Howard, R.~E., Hubbard,
  W.~E. \&  Jackel, L.~D.
\newblock {Handwritten digit recognition with a back-propagation network}.
\newblock In {\em Advances in neural information processing systems}, pages
  396--404, 1990.

\bibitem{krizhevsky2012imagenet}
Krizhevsky, A., Sutskever, I. \&  Hinton, G.~E.
\newblock {Imagenet classification with deep convolutional neural networks}.
\newblock In {\em Advances in neural information processing systems}, pages
  1097--1105, 2012.

\bibitem{zeiler2014visualizing}
Zeiler, M.~D. \&  Fergus, R.
\newblock {Visualizing and understanding convolutional networks}.
\newblock In {\em European conference on computer vision}, pages 818--833.
  Springer, 2014.

\bibitem{simonyan2014very}
Simonyan, K. \&  Zisserman, A.
\newblock {Very deep convolutional networks for large-scale image recognition}.
\newblock In {\em 3rd International Conference on Learning Representations,
  ICLR 2015 - Conference Track Proceedings}, San Diego, CA, United states,
  2015.

\bibitem{szegedy2015going}
Szegedy, C., Liu, W., Jia, Y., Sermanet, P., Reed, S., Anguelov, D., Erhan, D.,
  Vanhoucke, V. \&  Rabinovich, A.
\newblock {Going deeper with convolutions}.
\newblock In {\em Proceedings of the IEEE conference on computer vision and
  pattern recognition}, pages 1--9, 2015.

\bibitem{he2016deep}
He, K., Zhang, X., Ren, S. \&  Sun, J.
\newblock {Deep residual learning for image recognition}.
\newblock In {\em Proceedings of the IEEE conference on computer vision and
  pattern recognition}, pages 770--778, 2016.

\bibitem{xie2017aggregated}
Xie, S., Girshick, R., Doll{\'{a}}r, P., Tu, Z. \&  He, K.
\newblock {Aggregated residual transformations for deep neural networks}.
\newblock In {\em Proceedings of the IEEE conference on computer vision and
  pattern recognition}, pages 1492--1500, 2017.

\bibitem{szegedy2016inception}
Szegedy, C., Ioffe, S., Vanhoucke, V. \&  Alemi, A.~A.
\newblock {Inception-v4, inception-ResNet and the impact of residual
  connections on learning}.
\newblock In {\em 31st AAAI Conference on Artificial Intelligence, AAAI 2017},
  pages 4278--4284, San Francisco, CA, United states, 2017.

\bibitem{huang2016deep}
Huang, G., Sun, Y., Liu, Z., Sedra, D. \&  Weinberger, K.~Q.
\newblock {Deep networks with stochastic depth}.
\newblock In {\em European conference on computer vision}, pages 646--661.
  Springer, 2016.

\bibitem{lu2007survey}
Lu, D. \&  Weng, Q.
\newblock {A survey of image classification methods and techniques for
  improving classification performance}.
\newblock {\em International journal of Remote sensing}, 28(5):823--870, 2007.

\bibitem{cui2020revisiting}
Cui, Y., Che, W., Liu, T., Qin, B., Wang, S. \&  Hu, G.
\newblock {Revisiting Pre-Trained Models for Chinese Natural Language
  Processing}.
\newblock In {\em Findings of EMNLP}. Association for Computational
  Linguistics, 2020.

\bibitem{he2017fine}
He, X. \&  Peng, Y.
\newblock {Fine-grained image classification via combining vision and
  language}.
\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
  Pattern Recognition}, pages 5994--6002, 2017.

\bibitem{reed2016learning}
Reed, S., Akata, Z., Lee, H. \&  Schiele, B.
\newblock {Learning deep representations of fine-grained visual descriptions}.
\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
  Pattern Recognition}, pages 49--58, 2016.

\bibitem{fernandez2014we}
Fern{\'{a}}ndez-Delgado, M., Cernadas, E., Barro, S. \&  Amorim, D.
  Amorim.
\newblock {Do we need hundreds of classifiers to solve real world
  classification problems?}
\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
  2014.

\bibitem{kim2014convolutional}
Kim, Y.
\newblock {Convolutional neural networks for sentence classification}.
\newblock In {\em EMNLP 2014 - 2014 Conference on Empirical Methods in Natural
  Language Processing, Proceedings of the Conference}, pages 1746--1751, Doha,
  Qatar, 2014.

\end{thebibliography}
}
